---
title: "AssaySpecificity"
author: "TaylorWilcox"
date: "October 3, 2023"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
require(MASS)
require(dplyr)
```

## Load data
Input data should have columns: Genus, Species,	AP

```{r}
data <- read.csv(file.choose())
group_by(data, Genus) %>% summarize(N = n(), MeanAP = mean(AP))
```

## Estimate beta probability density function
```{r, include=FALSE}
family <- sample(data$AP, size = 500, replace = T)     
beta <- fitdistr(family, densfun = "beta", start = list(shape1 = 2, shape2 = 2))
```

```{r}
beta
```

## Histogram and inferred probability density function

Observed eDNAssay assignment probabilities are shown in the histogram. 
```{r, echo=FALSE}

### Plot
hist(data$AP, add = F, col = "darkorange", freq = F, xlim = c(0, 1),
     main = "", xlab = "eDNAssay AP")

lines(dbeta(seq(0,1,0.01), 
            shape1 = beta$estimate[1], 
            shape2 = beta$estimate[2]) ~ seq(0,1,0.01),
      lwd = 2, col = "blue")

abline(v = 0.30, col = "red", lty = 2)
abline(v = 0.50, col = "red", lty = 2)

### Table
mid_030 <- round(1 - pbeta(0.30, shape1 = beta$estimate[1], shape2 = beta$estimate[2]), 3)
mid_050 <- round(1 - pbeta(0.50, shape1 = beta$estimate[1], shape2 = beta$estimate[2]), 3)

summary_matrix <- matrix(c(mid_030, mid_050), 
                         nrow = 2, ncol = 1)

colnames(summary_matrix) <- c("Estimate")
rownames(summary_matrix) <- c("0.30 threshold", "0.50 threshold")
```

## Summary table
Table showing estimated probability of an unsampled confamilial exceeding an assignment probability thershold of 0.30 (first row) or 0.50 (second row) using probability density functions.

```{r, echo=FALSE}
summary_matrix
```